Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2020-11-30 draft_rsfmri.Rmd
change in reward network section

<!-- Potential mechanisms? -->
Precise mechanisms are yet to be elucidated. As a first step, a comprehensive understanding of the concurrent physiological changes underlying weight loss and recovery is needed. This will inform inferences about potential mechanisms and either support interventions proven to be effective or ideally allow imitating them will less invasive alternatives.

@@

<!-- Reward network -->
Little is known about the potential beneficial effects of bariatric surgery on brain function in the obese population, in particular with regard to hedonic motivations for food, which play a fundamental role in weight relapse.
<!-- mechanism reward and appetite, overating -->
Besides malabsorption and restricted food ingestion, patients report post-surgical changes in food preferences and eating behavior. Those psychophysiological and behavioral effects may be related to post-surgical changes in visceral sensory perceptions and endocrinological signaling. Corresponding information is processed by the fronto-mesolimbic system and affects appetite and reward signalling which a sustainable weight loss [@Mulla_2017, @Nudel_2019].

Several studies have demonstrated differences in resting-state activity in reward regions depending on weight status.

Obese individuals exhibited increased connectivity between frontal and mesolimbic regions and weaker connectivity within regions of the mesolimbic system (encompassing limbic and striatal regions). These differences seemed to normalize, as trends reversed when looking at the resting state of obese individuals after compared to before the surgery [@Duan_2020].

<!-- saliency and reward -->
In lean participants, food valuation processes in decision-making have been linked to brain activity and activity within the reward network, including ventromedial prefrontal cortex (vmPFC), the striatum (STR) but also the anterior insula (antIns) [@Bartra_2013; @Hare_2011; @Hutcherson_2012; @Schmidt_2018; @Wiemerslage_2016].

>>>>

<!-- Neural mechanisms/concurrent plasticity? -->
Precise mechanisms are yet to be elucidated. As a first step, a comprehensive understanding of the concurrent physiological changes underlying weight loss and recovery is needed. This will inform inferences about potential mechanisms and either support interventions proven to be effective or ideally allow imitating them will less invasive alternatives.

@@

<!-- Reward network -->
Little is known about the potential beneficial effects of bariatric surgery on brain function in the obese population, in particular with regard to hedonic motivations for food, which play a fundamental role in weight relapse.
<!-- mechanism reward and appetite, overating -->
Besides malabsorption and restricted food ingestion, patients report post-surgical changes in food preferences and eating behavior. Those psychophysiological and behavioral effects may be related to post-surgical changes in visceral sensory perceptions and endocrinological signaling. Corresponding information is processed by the fronto-mesolimbic system and affects appetite and reward signalling which may influence weight regulation [@Mulla_2017, @Nudel_2019].
The reward network entailing the ventromedial prefrontal cortex (vmPFC), the striatum (STR) but also the anterior insula (antIns) has been linked to food valuation processes in deciision-making in lean individuals [@Bartra_2013; @Hare_2011; @Hutcherson_2012; @Schmidt_2018; @Wiemerslage_2016].
<!-- study results -->
Accordingly, several studies have found differences in resting-state activity in reward regions depending on weight status.
Obese individuals exhibited increased connectivity between frontal and mesolimbic regions and weaker connectivity within regions of the mesolimbic system (encompassing limbic and striatal regions). These differences seemed to normalize, as trends reversed when looking at the resting state of obese individuals after compared to before the surgery [@Duan_2020].

On the other hand, BMI prior to the surgery was associated with changes in connectivity [@Duan_2020].

<!-- saliency and reward -->
